---
title: "Descriptive_Stats"
author: "Ruyuan Wan"
date: "7/30/2019"
output: word_document
---
```{r, echo= FALSE,message = FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)

```

```{r Upload datsets,echo= FALSE,message = FALSE}
setwd("C:/Users/respartintern2/OneDrive - The Michael J. Fox Foundation for Parkinson's Research/Ruyuan")
#read datasets
#Users_LTV<-read.csv("./Transformed Data/LTV_final.csv")
#Version 2: 1 point for genetic information
Users_LTV<-read.csv("./Transformed Data/LTV_final_G1pt.csv")
Users<-read.csv("./Raw Data/Users.csv")
Users_about<-read.csv("./Raw Data/About.csv")

```
# 1.a Age: data transformation##
```{r Age: data transformation, echo=FALSE,message = FALSE}
#BY age
LTV_Age<- Users_LTV %>%
        left_join(Users)%>%
        mutate(InitPDDiag<- factor(InitPDDiag))
LTV_18<-LTV_Age%>%
        filter(age<18)
LTV_18_34<- LTV_Age %>%
        filter(age>=18 & age< 34)
LTV_34_50<- LTV_Age %>%
        filter(age>=34 & age< 50)
LTV_50_69<- LTV_Age %>%
        filter(age>=50 & age< 69)
LTV_69_87<- LTV_Age %>%
        filter(age>=69 & age< 87)
LTV_87<- LTV_Age %>%
        filter(age>=87)
LTV_Age_factor <- LTV_Age %>%
        mutate(Age_group = case_when( age<18 ~ "[0,18)", age>=18 & age< 34 ~ "[18, 34)",
                                      age>=34 & age< 50 ~ "[34,50)", age>=50 & age< 69 ~ "[50,69)",
                                      age>=69 & age< 87 ~"[69,87)", age>=87 ~ "age>=87", TRUE ~ "NA"
        ))%>%
        slice(-1:-25)

```

# 1.b Age: discriptive statistics
```{r Age: descriptive statistics, echo=FALSE,message = FALSE}
ggplot(LTV_Age_factor, aes(x=Age_group, y=ltv)) +
  geom_boxplot() 


mean(LTV_18_34$ltv)
mean(LTV_34_50$ltv)
mean(LTV_50_69$ltv)
mean(LTV_69_87$ltv)
mean(LTV_87$ltv)

var(LTV_18_34$ltv)
var(LTV_34_50$ltv)
var(LTV_50_69$ltv)
var(LTV_69_87$ltv)
var(LTV_87$ltv)

quantile(LTV_18_34$ltv)
quantile(LTV_34_50$ltv)
quantile(LTV_50_69$ltv)
quantile(LTV_69_87$ltv)
quantile(LTV_87$ltv)
```
```{r output data, echo=FALSE}
write.csv(LTV_Age_factor,"LTV_Age_Factor.csv")

```

# 2.a Gender: data transformation
```{r Gender: data transformation, echo=FALSE,message = FALSE}
#By sex
LTV_Sex<-Users_LTV %>%
        left_join(Users_about)%>%
        distinct(fox_insight_id,.keep_all = TRUE)%>%
        mutate(Sex<-factor(Sex))%>%
        select(c("fox_insight_id","Sex","ltv"))
LTV_female<-LTV_Sex %>%
        filter(Sex == 2)%>%
        select(c("fox_insight_id","Sex","ltv"))
LTV_male<-LTV_Sex %>%
        filter(Sex == 1)%>%
        select(c("fox_insight_id","Sex","ltv"))
```
# 2.b Gender: descriptive statistics
```{r Gender: descriptive statistics, echo=FALSE,message = FALSE}
mean(LTV_female$ltv)
mean(LTV_male$ltv)

var(LTV_female$ltv)
var(LTV_male$ltv)

quantile(LTV_female$ltv)
quantile(LTV_male$ltv)

LTV_Sex_factor <- LTV_Sex %>%
        mutate(Sex = case_when(Sex == 1 ~ "male", Sex == 2 ~"female", TRUE ~"NA"))
        
ggplot(LTV_Sex_factor, aes(x=Sex, y=ltv)) +
  geom_boxplot()
```
```{r output, echo=FALSE}
write.csv(LTV_Sex_factor,"LTV_SEX_Factor.csv")
```

# 3.a Stage of disease: data transformation
```{r Stage of disease: data transformation, echo= FALSE,message = FALSE }

#stage of disease 
LTV_disease<- Users_LTV %>%
           left_join(Users)%>%
           mutate(PDstage = case_when(InitPDDiag== "1" ~  (age-InitPDDiagAge), TRUE ~ 0 )  )%>% 
           filter((InitPDDiag =="1"& InitPDDiagAge >20) | (InitPDDiag != 1 ))%>%
           slice(-1:-25)      
       #    select(c("fox_insight_id","ltv","PDstage","InitPDDiag","age","Ii"))
LTV_disease_CTR<- LTV_disease%>%  
           filter(PDstage==0)%>%
           select(c("fox_insight_id","ltv","PDstage"))

LTV_disease_2<- LTV_disease%>%  
           filter(PDstage> 0 & PDstage<=2 )%>%
           select(c("fox_insight_id","ltv","PDstage"))

LTV_disease_2_5<- LTV_disease%>%  
           filter(PDstage>2 & PDstage <=5 )%>%
           select(c("fox_insight_id","ltv","PDstage"))

LTV_disease_5_10<- LTV_disease%>%   
           filter(PDstage>5 & PDstage <=10)%>%
           select(c("fox_insight_id","ltv","PDstage"))

LTV_disease_10<- LTV_disease%>%  
           filter(PDstage>10 )%>%
           select(c("fox_insight_id","ltv","PDstage"))

```

# 3.b Stage of disease: descriptive statistics
```{R Stage of disease: descriptive statistics, echo = FALSE,message = FALSE}
mean(LTV_disease_CTR$ltv)
mean(LTV_disease_2$ltv)
mean(LTV_disease_2_5$ltv)
mean(LTV_disease_5_10$ltv)
mean(LTV_disease_10$ltv)

var(LTV_disease_CTR$ltv)
var(LTV_disease_2$ltv)
var(LTV_disease_2_5$ltv)
var(LTV_disease_5_10$ltv)
var(LTV_disease_10$ltv)

quantile(LTV_disease_CTR$ltv)
quantile(LTV_disease_2$ltv)
quantile(LTV_disease_2_5$ltv)
quantile(LTV_disease_5_10$ltv)
quantile(LTV_disease_10$ltv)

LTV_disease_factor <- LTV_disease %>%
        mutate(PD_stage_group = case_when(PDstage==0 ~ "healthy control",PDstage>0 & PDstage <=2 ~ "(0,2]",PDstage>2 & PDstage <=5 ~ "(2,5]", 
                                    PDstage>5 & PDstage <=10 ~ "(5,10]", PDstage>10 ~ "10+",
                                 TRUE ~ "" ))
ggplot(LTV_disease_factor, aes(x=PD_stage_group, y=ltv)) +
  geom_boxplot()

```


```{r output, echo= FALSE}
write.csv(LTV_disease_factor,"LTV_disease_factor.csv")
```
The longest stage of disease is 50.8. Participant "FOX_008122" was diagnoed at 40 years old. 

# 4.a  Covariate Relationship: data transformation
```{r Covariate Relationship: data transformation, echo=FALSE,message = FALSE}
Users_Age_PDstage<-LTV_disease %>%
           left_join(LTV_Age)
Users_Age_Sex <- LTV_Sex %>%
           left_join(LTV_Age)

Users_PDstage_Sex <- LTV_disease %>%
           left_join(LTV_Sex)
Users_PDstage_Sex<-na.omit(Users_PDstage_Sex)

PDstage_male<-Users_PDstage_Sex[which(Users_PDstage_Sex$Sex ==1),]
PDstage_female<-Users_PDstage_Sex[which(Users_PDstage_Sex$Sex ==2),]

Age_male<-Users_Age_Sex[which(Users_Age_Sex$Sex == 1),]
Age_female<- Users_Age_Sex[which(Users_Age_Sex$Sex == 2),]
```

# 4.b Covariate Relationship: correlation test
```{r Covariate Relationship: correlation test, echo= FALSE,message = FALSE}

cor.test(Users_Age_PDstage$PDstage,Users_Age_PDstage$age,alternative = "greater")

wilcox.test(PDstage_male$PDstage,PDstage_female$PDstage ,alternative = "greater"  )

wilcox.test(Age_male$age,Age_female$age ,alternative = "greater" )

```

There are significant corelation between each two variables between age, sex and stage of disease.  

# 5 Enrollment Time 
```{r echo=FALSE,message = FALSE}
#enrollment time
Users_enrollment<-Users%>%
        mutate(Engagetime= Users$age - Users$AgeAtEnrollment)
Users_enrollment<- na.omit(Users_enrollment)
quantile(Users_enrollment$Engagetime)
mean(Users_enrollment$Engagetime)
```

Mean of the time that participants engaged in this study is 0.7631175 year. 

